### 2014-03-08 src/analysis.Rnw
udpate

For comparing between different techniques, we ran correlation analysis between the full mutation score,
and that produced by the reduction criteria. Further, we also collected the mean reduction, and the standard
deviation of the reduction across all the projects for both randoop and original. These statistics are provided below.
\subsection{Analysis of Sampling Criteria}
% We have power, element, kind(O/R), and MuRed, MuRedSD, R^2
\subsubsection{x\% selection}
<<xpercentunit>>=
sel.colnames <- c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier')
new.colnames <- c('operator', 'r^2',      'm.red',            'm.sd',         'num',    'B*')
stats.xp <- subset(stats.df, grepl('^(r|rr|rc)[.]', operator))

o.stats.sel.xp <- subset(o.f(stats.xp), select=sel.colnames)
r.stats.sel.xp <- subset(r.f(stats.xp), select=sel.colnames)
stats.rest <- subset(stats.df, !grepl('^(r|rr)[.]', operator)) # We are ignoring ceil here. add rc if needed.
colnames(o.stats.sel.xp) <- new.colnames
colnames(r.stats.sel.xp) <- new.colnames

>>>>

For comparing between different techniques, we ran correlation analysis between the full mutation score,
and that produced by the reduction criteria. Further, we also collected the mean reduction, and the standard
deviation of the reduction across all the projects for both randoop and original. These statistics are provided below.
\subsection{Analysis of Sampling Criteria}
% We have power, element, kind(O/R), and MuRed, MuRedSD, R^2
\subsubsection{x\% selection}
<<xpercentunit>>=
sel.colnames <- c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier')
new.colnames <- c('operator', 'r^2',      'm.red',            'm.sd',         'num',    'B*')
stats.xp <- subset(stats.df, grepl('^(r|rr)[.]', operator)) # We are ignoring ceil here. add rc if needed.

o.stats.sel.xp <- subset(o.f(stats.xp), select=sel.colnames)
r.stats.sel.xp <- subset(r.f(stats.xp), select=sel.colnames)
stats.rest <- subset(stats.df, !grepl('^(r|rr|rc)[.]', operator))
colnames(o.stats.sel.xp) <- new.colnames
colnames(r.stats.sel.xp) <- new.colnames
